\textbf{CMCS 818J Project Final Report}

### 2012-12-20 doc/final_report/draft_report.tex
Rough draft finished

	The implementation in its current state as of this writing consists of two Ruby classes and one Ruby module.
	The classes are, not surprising, Prover and Verifer and the module is named Sads.
	Ruby has a feature called \textit{mixing} in which a module can be "mixed into" a class.
	Mixing in a module has the effect of include all the modules fields and methods into the class definition.

	\subsection{Underlying Data Structures}

		A crucial component of the SADS algorithm relies on matrix multiplication, a relatively expensive computational operation.
		When formulating our plan of action for this project, we were recommended a few linear algebra libraries, which will be discussed in a later section.
		While we recognize the importance of fast matrix operations and parallelism for production quality code, we thought that the added complexity, as well as unknowns with respect to implementation details, would be prohibitive.
		Instead, we've decided to use an interpreted language and the simple matrix operations that come with the standard libraries to start.

	\subsection{SADS Scheme}

	Once the underlying data structure is complete, the SADS scheme will use it as a primitive.
	Though one of the scheme's strengths is the independence of the prover and verifier during the streaming setting, the two parties will necessarily need to communicate during the query phase.
	Additionally, there may be communication between the two parties to initiate the streaming setting.
	For these reasons, we anticipate creating an application which will require network communication as it will likely be the case that the verifier and prover are not collocated.

	%We have a few frameworks in mind for this task.
	%Two of our options at the moment are EventMachine and Node.js.
	%Node.js is a "platform for building fast, scalable network applications" and has been gaining popularity in the Ruby community. http://nodejs.org/
	%EventMachine is a "fast, simple event-processing library for Ruby programs."http://rubyeventmachine.com/

@@

	We ran some preliminary calculations to ballpark the size of matrices L and R, the public key of the SADS scheme.
	Recall that L and R are matrices with elements in $Z_q$, that is elements are integers of at most q and q is derived from the security parameter, k and the upper bound on the size of the stream, n.
	So a rough estimate of the size of L and R can be calculated by multiplying the dimensions of the matrices, by the amount of space required for each element.
	Below are two tables of estimations.

@@

	\caption{Estimation of public key size.  Constant stream size upper bound , varying security parameter } 
	\label{tab:pub-key_k}
	\end{table}

@@

		\end{tabular}
	\caption{ Estimation of public key size.  Constant security parameter, varying stream size upper bound }
	\label{tab:pub-key_n}
	\end{table}

>>>>

	The implementation in its current state as of this writing consists of two Ruby classes and one Ruby module.
	The classes are, not surprising, Prover and Verifier and the module is named Sads.
	Ruby has a feature called \textit{mixins} in which a module can be "mixed into" a class.
	Mixing in a module has the effect of include all the modules fields and methods into the class definition.
	The Sads module contains any pieces of functionality required by both the Prover and the Verifier - the definition of the hash function for example.
	However since an instantiation of a Sads would not make sense, module mix in is used instead of class inheritance.
	The Prover and Verifier classes then mix in the functionality defined in Sads augmenting the Prover-only or Verifier-only functionality defined in their respective classes.
		Future iterations of this library will include a stronger focus on object-oriented design especially surrounding the nodes of the tree stored by the prover, the proofs generated per query requests, and abstractions surrounding the matrix multiplication so various linear algebra implementations can be tested.

	The next stage was to implement streaming setting in which the Prover and Verifier operate independently while witnessing a common stream of data.
	We wrote a very simple script to simulate such a scenario.
	This script was created as a new project, also using Ruby, and installed the SADS library via the RubyGems command 'gem install --local'.
	We wanted to ensure that the steps we took to use the SADS library in another project were the same or close to what other developers might do when using our library.
	The script takes three parameters to initialize the entire protocol, the security parameter, the upper bound on the size of the stream, and the size of the universe of stream elements.
	The Prover can be initialized from just these three parameter.
	The Verifier is then initialized with parameters provided to it from the Prover, similar to a client-server initialization wherein a client requests a session from a web server and can only proceed once the server grants the client the credentials.
	Finally in this small example, the user is then able to run commands such as "add" which simulates the Prover and Verifier both witnessing some stream element or "query" which simulates a membership query from the Verifier to the Prover.

	The final stage is to implement the simulation across distributed computing infrastructure, that is a Prover and Verifier non-co-located.
	We imagine at least two possibilities for this implementation.
	One possibility could be a web service could be created that plays matchmaker between "needy" clients requesting prover services and "generous" clients wishing to act as a prover.
	Another possibility, similar to the first, is one in which the web service itself acts as a Prover for any client requesting service.
	In either of these scenarios we imagine deploying a server application possibly build in EventMachine or Node.js or some similar framework.
	Some proposed applications include monitoring and verifying of bandwidth charges from an ISP or continuous sensor data.

@@

	We ran some preliminary calculations to ballpark the size of matrices \textbf{L} and \textbf{R}, the public key of the SADS scheme.
	Recall that \textbf{L} and \textbf{R} are matrices with elements in $Z_q$, that is elements are integers of at most $q$, which is itself derived from the security parameter, $k$ and the upper bound on the size of the stream, $n$.
	So a rough estimate of the size of \textbf{L} and \textbf{R} can be calculated by multiplying the dimensions of the matrices, by the amount of space required for each element.
	Below are two tables of estimations.

@@

	\caption{Estimation of public key size.  Constant stream size upper bound, varying security parameter } 
	\label{tab:pub-key-k}
	\end{table}

@@

		\end{tabular}
	\caption{ Estimation of public key size. Constant security parameter, varying stream size upper bound }
	\label{tab:pub-key-n}
	\end{table}
